The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-13 analysis/paper/paper.qmd
Update topic model script with different Ks

# Extract beta and theta statistics from LDA model
beta <- posterior(emu_lda)$terms
theta <- posterior(emu_lda)$topics

# Preview 10 terms from each topic
terms(emu_lda, 10)

# Add pseudo-names to topics based on the top 5 words in each topic
topic_names <- name_topics(beta)

@@

# TODO Replace this with a table containing topics, documents, and theta
#      sorted by theta in decreasing order
# What is the dominant topic in each document?
N = 82
topic_prop_examples <- theta[1:N,]
colnames(topic_prop_examples) <- str_sub(topic_names, 1, 40)
# TODO change to pivot_longer
vizDataFrame <- melt(cbind(data.frame(topic_prop_examples), 
                           document = factor(str_sub(rownames(topic_prop_examples), 1, 20))), 
                     variable.name = "topic", id.vars = "document")  
ggplot(data = vizDataFrame, aes(topic, value), ylab = "proportion") + 
  geom_bar(stat="identity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +  
  coord_flip() +
  facet_wrap(~ document, ncol = 5) +
  theme(legend.position = "none")

vizDataFrame |> 
  group_by(document) |> 
  mutate(value_max = max(value),
         topic_max = topic[value == value_max])

>>>>

# Extract beta and theta statistics from LDA model
beta_5 <- posterior(emu_lda_5)$terms
theta_5 <- posterior(emu_lda_5)$topics

beta_k <- posterior(emu_lda_k)$terms
theta_k <- posterior(emu_lda_k)$topics

# Add pseudo-names to topics based on the top 5 words in each topic
topic_names_k <- name_topics(beta_k)
topic_names_5 <- name_topics(beta_5)

@@

# TODO Replace this with a table containing topics, documents, and theta
#      sorted by theta in decreasing order
# What is the dominant topic in each document?
N = 70
topic_prop_examples <- theta_5[1:N,]
colnames(topic_prop_examples) <- topic_names_5
# TODO change to pivot_longer
vizDataFrame <- melt(cbind(data.frame(topic_prop_examples), 
                           document = factor(str_sub(rownames(topic_prop_examples), 1, 20))), 
                     variable.name = "topic", id.vars = "document") |> 
  group_by(document) |> 
  mutate(value_max = max(value),
         topic_max = topic[value == value_max])
ggplot(data = vizDataFrame, aes(topic, value, fill = topic_max), ylab = "proportion") + 
  geom_bar(stat="identity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +  
  coord_flip() +
  facet_wrap(~ document, ncol = 10) +
  theme(legend.position = "bottom") +
  scale_fill_viridis_d(name = "Topic") +
  labs(title = "Theses as distributions over topics",
       subtitle = "Charts colored by the highest probability")
